What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Example of slot lookup

%TODO Add a simple example of a slot lookup (very common with match.call)

@@

\paragraph{Injecting code in package environments.} R distinguishes two kinds of environments for packages: the \emph{package} environment itself, which contains every publicly accessible functions, and the \emph{namespace} environment, which contains all functions including private ones.

>>>>

%TODO Add a simple example of a slot lookup (very common with match.call)
Slot lookup happens very often to evaluate some of the elements of a call list returned by \c{match.call}.
For instance in the \emph{blme} package:
\begin{lstlisting}
matchedCall <- match.call()
...
df <- eval(matchedCall$df)
\end{lstlisting}

\mypara{Assigment \c{<-}.}

@@

\mypara{Injecting code in package environments.} R distinguishes two kinds of environments for packages: the \emph{package} environment itself, which contains every publicly accessible functions, and the \emph{namespace} environment, which contains all functions including private ones.
